---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# rsicons

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/rundel/rsicons/workflows/R-CMD-check/badge.svg)](https://github.com/rundel/rsicons/actions)
<!-- badges: end -->

The goal of `rsicons` is to make the various icons used within the RStudio IDE available as images that can be embedded in other projects (e.g. RMarkdown documents, Shiny apps, etc.)

## Installation

<!--
You can install the released version of rsicons from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rsicons")
```
-->

The development version can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rundel/rsicons")
```
## Example

The core function of the package is `icon()` which lets you insert a named icon in a chunk 

```{r example}
library(rsicons)
icon("rstudio", height=64)
```

, via inline code `r icon("rstudio", height = 24)`, or any where else you can embed an image. 

Details about each icon can be obtained via the `icon_info()` function,

```{r info}
icon_info("rstudio")
```



### Available Icons

A listing of currently available icons can be obtained with `available_icons()`, this listing can be refined by providing a `pattern` which uses regular expressions to match the icon names,
```{r av_icon}
available_icons(pattern = "vcs")
```

Similarly, a list of all available types can obtained with,
```{r av_type}
available_types()
```

If instead you would would more directly like to view the available icons, you can use the preview functions:

```{r pr_icon}
preview_icon("application-x-r-project")
```

```{r pr_type}
preview_type("File")
```

### All Current Icons

```{r pr_all, echo=FALSE}
preview_all(n_col = 3)
```
