---
title: "Get started with **rsicons**"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The **rsicons** package allows you to insert icons from the RStudio IDE into your R Markdown documents and Shiny applications easily with one function: `icon()`. 
This might be particularly useful for documents designed for teaching and/or documentation as it allows you to avoid the pesky "take a screenshot and insert into your document" step.
You can insert the logos as stand-alone images or inline.

```{r setup}
library(rsicons)
```

## Inserting icons

For example, if you insert the following in an R Markdown document:

```{r eval = FALSE}
Click on `r icon("mermaid", height = 16)` to create a new branch.
```

You'll get the following output when you knit your document:

---

Click on `r icon("mermaid", height = 16)` to create a new branch.

---

You can also insert images on their own. 
By default, rsicons will use the closest size available for the `height` you specify. 
For example, in the output below, we specify `height = 100` but the image that's displayed is 128x128.

```{r}
icon("rstudio", height = 100)
```

To get the precise height you want, use `resize = TRUE`.

```{r}
icon("rstudio", height = 100, resize = TRUE)
```

## Icon information

You can get information on any of the icons with `icon_info()`. 
This is especially helpful for figuring out available sizes.

```{r}
icon_info("rstudio")
```

## Available icons

A listing of currently available icons can be obtained with `available_icons()`, this listing can be refined by providing a `pattern` which uses regular expressions to match the icon names with the `pattern` argument.

```{r av_icon}
available_icons(pattern = "vcs")
```

Similarly, a list of all available types can obtained with `available_types()`.

```{r av_type}
available_types()
```

If instead you would would more directly like to view the available icons, you can use the preview functions:

```{r pr_icon}
preview_icon("application-x-r-project")
```

```{r pr_type}
preview_type("File")
```
